Optimal Strategies for Target Volatility Contracts

### 2021-04-07 tex/targetvol.tex
new tex

\usepackage[]{hyperref}
\hypersetup{
	colorlinks=true,breaklinks=true,
	urlcolor= mydarkblue,linkcolor= mydarkblue,citecolor= mydarkgreen,
	pdfauthor={Daluiso, R., Pallavicini, A.},
}
\usepackage{natbib}
\setcitestyle{authoryear,open={(},close={)}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{remark}{Remark}[section]
\newtheorem{example}[remark]{Example}

@@

\begin{proposition}
When the underlying securities follow a Black and Scholes model with deterministic rates, the optimal strategy for a monotone payoff consists in minimizing the local drift function, indipendently of the current state $I_t$
\begin{equation}
    \alpha^*(t) \coloneqq \argmin_\alpha \frac{\alpha \cdot \mu(t)}{\|\alpha \cdot \nu(t) \|}.
\label{eq:BS_optimal_strategy}\end{equation}
\end{proposition}
The absence of stochastic elments in \Cref{eq:BS_optimal_strategy} makes the optimal strategy known \textit{a priori}; in fact one can solve the optimization problema once for all for each $t \in \mathcal{T}$ just looking at the market data $\mu(t)$ and $\nu(t)$ for the securities. Once $\alpha^*$ is known, then one can price the payoff by Monte Carlo simulation. 
\subsubsection{Closed form solution for free strategy}
In absence of constraints on $\alpha \coloneqq \alpha(t)$, the problem even admits a closed form solution. We set $\mu \coloneqq \mu(t)$ and $\nu \coloneqq \nu(t)$. By homogeneity we can rewrite \eqref{eq:BS_optimal_strategy} as
\begin{equation}
	\boxed{
		\begin{aligned}
			&\text { minimize } \alpha \cdot \mu\\
			&\text { subject to } \|\alpha \cdot \nu\|^2=1
	\end{aligned}}
\end{equation}
By setting the Lagrangian function associated with the problem
\begin{equation}
	\mathcal{L}\left(\alpha, \lambda\right)=\alpha \cdot \mu-\lambda\left(\|\alpha \cdot \nu\|^2-1\right) \, ,
\end{equation}
we obtain the first order conditions
\begin{eqsys}
	\frac{\partial \mathcal{L}}{\partial \alpha}=\mu -2\lambda \Sigma \cdot \alpha=0 \\
	\frac{\partial \mathcal{L}}{\partial \lambda}= \|\alpha \cdot \nu\|^2-1=0
	\, ,
\end{eqsys}
where we have set $\Sigma = \nu  \nu^T$, with $\nu^T$ the transpose matrix of $\nu$.
Then, by applying simple algebra, we obtain the analytical form of the free optimal strategy
\begin{equation}
	\alpha^* = \pm \frac{\Sigma^{-1} \cdot \mu}{\|(\Sigma^{-1} \cdot \mu)\cdot \nu\|}
\end{equation}
We take the minus sign to get the minimum value of the TVS local drift.

In our work the definition of $\alpha$ is general, thus it is possible to consider the case of constrained allocation strategy; in this case the problem \eqref{eq:BS_optimal_strategy} must be solved numerically.
\subsubsection{Active Asset (or Bang Bang) Solution}
A closed form solution to the minimization of the local drift correction \eqref{eq:BS_optimal_strategy} can also be derived in the common case that all costs of carry are nonnegative and the only constraint on portfolio weights is nonnegativity, which would mean a long only strategy by the fund manager.

@@

 We adopt as learning strategy the PPO algoritm developed in \cite{ppo} and \cite{gae}. 
\cleardoublepage
\bibliographystyle{abbrvnat}
\bibliography{Bib}
\end{document}

>>>>

\usepackage[]{hyperref}
\hypersetup{
	colorlinks=true,breaklinks=true,
	urlcolor= mydarkblue,linkcolor= mydarkblue,citecolor= mydarkgreen,
	pdfauthor={Daluiso, R., Pallavicini, A.},
}
\usepackage[backend=biber,style=authoryear-comp,maxcitenames=2,sorting=nyt,natbib=true,sortcites=false]{biblatex}
\addbibresource{Bib.bib}
%\usepackage{natbib}
%\setcitestyle{authoryear,open={(},close={)}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{remark}{Remark}[section]
\newtheorem{example}[remark]{Example}

@@

\begin{proposition}
When the underlying securities follow a Black and Scholes model with deterministic rates, the optimal strategy for a monotone payoff consists in minimizing the local drift function, indipendently of the current state $I_t$
\begin{equation}
    \alpha^*(t) \coloneqq \argmin_\alpha \frac{\alpha \cdot \mu(t)}{\|\alpha \cdot \nu(t) \|}.
\label{eq:BS_optimal_strategy}\end{equation}
\end{proposition}
The absence of stochastic elments in \Cref{eq:BS_optimal_strategy} makes the optimal strategy known \textit{a priori}; in fact one can solve the optimization problema once for all for each $t \in \mathcal{T}$ just looking at the market data $\mu(t)$ and $\nu(t)$ for the securities. Once $\alpha^*$ is known, then one can price the payoff by Monte Carlo simulation. 
\subsubsection{Black's Closed form solution}
In absence of constraints on the allocation strategy, we are able to derive a closed form solution to the BS problem \eqref{eq:BS_optimal_strategy}
\begin{lemma}
	Let be $\mu, \alpha \in \mathbb{R}^n$, $\nu \in \mathbb{R}^{n\times n}$ be a full rank matrix and $\Sigma\coloneqq \nu \nu^T$. Then the closed solution of the optimization problem \eqref{eq:BS_optimal_strategy} is 
	\begin{equation}
			\alpha^* = - \frac{\Sigma^{-1} \cdot \mu}{\|(\Sigma^{-1} \cdot \mu)\cdot \nu\|}
	\end{equation}
\end{lemma}
\begin{proof}
Since the argument of the minimum \eqref{eq:BS_optimal_strategy} is zero-homogeneous, then we can rewrite the problem as
\begin{equation}
		\begin{aligned}
			&\text { minimize } \alpha \cdot \mu\\
			&\text { subject to } \|\alpha \cdot \nu\|^2=1
	\end{aligned}
\end{equation}
By setting the Lagrangian function associated with the problem
\begin{equation}
	\mathcal{L}\left(\alpha, \lambda\right)=\alpha \cdot \mu-\lambda\left(\|\alpha \cdot \nu\|^2-1\right) \, ,
\end{equation}
we obtain the first order conditions
\begin{eqsys}
	\frac{\partial \mathcal{L}}{\partial \alpha}=\mu -2\lambda \Sigma \cdot \alpha=0 \\
	\frac{\partial \mathcal{L}}{\partial \lambda}= \|\alpha \cdot \nu\|^2-1=0
	\, ,
\end{eqsys}
Then, by applying simple algebra, we obtain the analytical form of the free optimal strategy
\begin{equation}
	\alpha^* = \pm \frac{\Sigma^{-1} \cdot \mu}{\|(\Sigma^{-1} \cdot \mu)\cdot \nu\|}
\end{equation}
We take the minus sign to get the minimum value of the TVS local drift. 
\end{proof}
\subsubsection{Active Asset (or Bang Bang) Solution}
A closed form solution to the minimization of the local drift correction \eqref{eq:BS_optimal_strategy} can also be derived in the common case that all costs of carry are nonnegative and the only constraint on portfolio weights is nonnegativity, which would mean a long only strategy by the fund manager.

@@

 We adopt as learning strategy the PPO algoritm developed in \cite{ppo} and \cite{gae}. We have

\cleardoublepage
\printbibliography
\end{document}
